---
title: "Women's Soccer Data"
output: html_notebook
---

```{r}

```

```{r}

```

We'll use this notebook to explore some NCAA women's soccer data and [our questions](https://docs.google.com/spreadsheets/d/1kTSrnl1URmcexIWLDMWqDnp3q-c2OS45uifnhjp10n4/edit#gid=0). First, let's load the tidyverse library:

```{r}
library(tidyverse)
```

We'll want to start with 2023 match data, which is located in [this GitHub repository](https://github.com/dwillis/NCAAWomensSoccerData). We can load the match data directly from GitHub using `read_csv`:

load data and add a total goal column 
```{r}
matches_2023<- matches_2023 <- read_csv("https://raw.githubusercontent.com/dwillis/NCAAWomensSoccerData/main/data/ncaa_womens_soccer_matchstats_2023.csv") |> mutate(total_goals = goals + defensive_goals)

matches_2024<-matches_2024 <- read_csv("https://raw.githubusercontent.com/dwillis/NCAAWomensSoccerData/main/data/ncaa_womens_soccer_matchstats_2024.csv")|> mutate(total_goals = goals + defensive_goals)
```
T-test for the Ncaa
```{r}
result <- t.test(matches_2023$total_goals, matches_2024$total_goals, alternative= "two.sided", var.equal = TRUE)
print(result)

#Goals was up this year in 2024 compared to the year in 2024, The difference is statistically significant, meaning it’s unlikely to be due to random chance.  
```

Maryland's T-test 
```{r}
umd_total_goals23 <- matches_2023 |>
  filter(team == 'Maryland Terrapins, Terps') |> mutate(season=2023) 

umd_total_goals24 <- matches_2024 |>
  filter(team == 'Maryland Terrapins, Terps') |> mutate(season=2024)

result <- t.test(umd_total_goals23$total_goals, umd_total_goals24$total_goals, alternative= "two.sided", var.equal = TRUE)

print(result)

#The total goals was up in 2024 then in 2023, however the difference isn’t big enough to confidently say it’s a real change and not just something that could happen randomly.
```

Let's take a look at this data to see what it contains, using `head` and `glimpse`:

```{r}
head(matches_2023)
glimpse(matches_2023)
```

Now, onto the questions using aggregates, which means `group_by` and `summarize`:

1.  How many shots in total has Maryland attempted and how many have been on goal? Calculate a percentage of shots on goal. They attempted a total of 180 shots and had 77 shots on goal, the percentage of shots on goal is .428

```{r}
combined_data <-matches_2023 |>
  group_by(team) |>
  reframe( sh_att = sum(sh_att),
             so_g = sum(so_g))



```

2.  What about the same shot stats from last season's first four games? You'll need to load the matches from 2022 - just change the season in the URL - and filter by date to find the first four games. They attempted 48 shots for the first four games and had 23 shots on goals, making their shot shot on goal percentage .478

```{r}
matches_2022 <- read_csv("https://raw.githubusercontent.com/dwillis/NCAAWomensSoccerData/main/data/ncaa_womens_soccer_matchstats_2022.csv")

combined_data_for_2022 <-matches_2022|> 
  filter(team == "Maryland Terrpains, Terps") |>
  filter(date < '2022-09-02') |> group_by(team) |>
  reframe( sh_att = sum(sh_att), 
           so_g = sum(so_g))
  
```

3.  What about draws - Maryland started 2022 with 4 ties. Have any other teams had as many this season? No other team has had as many ties as Maryland in the first 4 games.

```{r}

draw_data <- matches_2022|> 
  filter(date < '2022-09-02') |> group_by(team,outcome) |>
  summarise(count= n ())
```

```{r}
matches_2024 <- read.csv("https://raw.githubusercontent.com/dwillis/NCAAWomensSoccerData/main/data/ncaa_womens_soccer_matchstats_2024.csv")

matches_2024 <- matches_2024 |> mutate(corner_ratio = corners/defensive_corners)


matches_2024|>
  filter(corner_ratio >= 4.0) |> group_by(outcome) |>
  summarise(count = n ())
```

```{r}

```

```         
```

4.  How many total corner kicks has Maryland had so far and how many have its opponents have? Calculate the difference between the two totals for every team. Maryland had 22 corner kicks and the total number of the opponents were 2611.

``` r
```{r} corner_kicks <- matches_2022|> filter(date < '2022-09-02') |> group_by(team) |> summarise(corners = sum(corners))|> mutate(corner_difference = corners/2633)
```

``` r
matches_2024 <- read_csv("https://raw.githubusercontent.com/dwillis/NCAAWomensSoccerData/main/data/ncaa_womens_soccer_matchstats_2024.csv")
```

```{r}
matches_2024 |>
  group_by(team) |>
  summarise( sh_att= sum(sh_att),
             so_g= sum(so_g),
             pct_goal_shots = so_g/sh_att)
```


```{r}

```

