### The question I choose to explore further is weather you be short in volleyball and still succeeded, specifically in the position of a D.S. or a Libero. The data does exisit and I will be using the  years 2022-2023, I got it through my professors github. However, I will have to workthrough the data and create new data sets that focus soley on D.S.'s  or a Libero's positions. I will have to figure out the average height for all teams within these positions, then I would have tp see how that compares to there in game play. There is an example of this type of data story: https://towardsdatascience.com/does-height-really-matter-c3db062e8333, but it focuses on weather height matters in the means of offense, not within the means of defense and  passing position. 

```{r}
library(tidyverse)
```

```{r}
matches23 <- read_csv("https://raw.githubusercontent.com/dwillis/NCAAWomensVolleyballData/main/data/ncaa_womens_volleyball_matchstats_2023.csv")

matches22 <- read_csv("https://raw.githubusercontent.com/dwillis/NCAAWomensVolleyballData/main/data/ncaa_womens_volleyball_matchstats_2022.csv")

rosters23 <- read_csv("https://raw.githubusercontent.com/Sports-Roster-Data/womens-volleyball/refs/heads/main/rosters_2023_cleaned.csv")

roster22 <- read_csv("https://raw.githubusercontent.com/Sports-Roster-Data/womens-volleyball/refs/heads/main/rosters_2022.csv")
```

