### The question I choose to explore further is weather you be short in volleyball and still succeeded, specifically in the position of a D.S. or a Libero. The data does exisit and I will be using the  years 2022-2023, I got it through my professors github. However, I will have to workthrough the data and create new data sets that focus soley on D.S.'s  or a Libero's positions. I will have to figure out the average height for all teams within these positions, then I would have tp see how that compares to there in game play. There is an example of this type of data story: https://towardsdatascience.com/does-height-really-matter-c3db062e8333, but it focuses on weather height matters in the means of offense, not within the means of defense and  passing position. 


###load libraries 
```{r}
library(tidyverse)
```

###load data
```{r}

player_stats <- read_csv("https://raw.githubusercontent.com/dwillis/NCAAWomensVolleyballData/refs/heads/main/data/ncaa_womens_volleyball_playerstats_2023.csv")

logs <- read_csv("https://dwillis.github.io/sports-data-files/ncaa_womens_volleyball_matchstats_2023.csv")
```

### Make a new column for total_inches for height
```{r}
player_stats <- player_stats |> 
  mutate(feet = as.numeric(feet), inches = as.numeric(inches)) %>%
  mutate(total_inches = (feet*12)+inches)
```



### Seperating the D.S. & Libero Positions 
```{r}
 player_stats |> group_by(pos) |> summarise(count = n())

player_stats <- player_stats |> mutate(newpos = case_when(grepl("DS", pos) ~ "DS",
                                          grepl("L", pos) ~ "L",
                                          grepl("L/DS", pos) ~ "DS"))



```
###Making a dataset that shows the average height for a DS, or L. and how many digs they have
```{r}
avg_height <- player_stats|> filter(newpos == newpos) |> group_by(team, digs) |> summarise(avg_height = total_inches) 


```
Looking at this data there are some crazy ouputs, the tallest recorded DS or L at 73 inches, only had a total of 9 digs!!!While the the smallest recorded D.S. or L at 59 inches, had a total of 89 digs.

###Plotting avg_height compared to digs
```{r}
ggplot() + geom_point(data=avg_height, aes(x=avg_height, y=digs))
```
This shows me that to pass in the sport of volleyball, you don't have to be tall. There is no significant pattern that shows height plays a factor on being able to pass, the data is all over the place. 


### Testing the avg_height compared to digs for all schools
```{r}
fit <- lm(digs ~ avg_height, data = avg_height)
summary(fit)
```
The model identifies a substantial but modest link between average_height and digs.
While the avg_height coefficient is significant at the 0.05 level, the extremely low R-squared value (0.0037) indicates that avg_height explains very little of the variance in digs, and other factors are likely to have a greater influence.

