```{r}
if (!requireNamespace('pacman', quietly = TRUE)){
  install.packages('pacman')
}
pacman::p_load_current_gh("sportsdataverse/recruitR")
```

For this notebook I will exploring my questions: Where do five star recruits usually come from? Which schools get the most five star recruits, and which ones don't? How do top ranked 5 stars play in their rookie season in the NFL? Also does a hot place like Floridia get more five stars than a cold place like Nebraska?

I will be ranging my data from the five star recruits in the years 2020-2023. The only thing that is not in my data that I will need to figure out is how to get the data to show how the top recruits did in their rookie season.

**loading data :**

```{r}
library(recruitR)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(maps)
library(tidycensus)
```

```{r}
recruitR::cfbd_recruiting_player

logs20 <- cfbd_recruiting_player(2020, recruit_type = 'HighSchool')


```

```{r}
states <- get_decennial(
  geography = "states",
  variables = c(totalpop = "P1_001N"),
  year = 2020
) |>
  arrange(desc(value))
```

```{r}
```


```{r}
logs20 <- logs20 |> group_by(stars = '5', name, school, committed_to,ranking, position,city, state_province, hometown_info_latitude, hometown_info_longitude) |> summarise(count=n())

```

```{r}
fivestars20 <- logs20 |> group_by(state_province) |> summarise(count= n())

```

Texas, Florida and California get frequent five star recruits.


Still need to: create code to show how top performers in these states did in their rookie seasons, 

Add a map graphic to show cold vs hot states, 
Add a bar chart to show top states. 
Add map graphic to show states number of recruits.
